ROBUST BAYESIAN RELIABILITY FOR COMPLEX SYSTEMS UNDER PRIOR-DATA CONFLICT

### 2016-07-29 asce-paper.tex
double space for submission
final edits for submission

\documentclass[Journal,SectionNumbers,SingleSpace,InsideFigs]{ascelike}

@@

%Invited for special issue ``The treatment of uncertainty in risk and reliability modelling and decision making''
%(special issue code SI022A), guest editors Luca Podolfillini, Bruno Sudret, Enrico Zio,
%in ASCE-ASME Journal of Risk and Uncertainty in Engineering Systems: Part A (Civil Engineering)
%
%***``For most ASCE journals, the maximum number of words and word-equivalents is 10,000 for technical papers''
%***Abstract must be 150--175 words long (this has 175), may not contain references or mathematics.
%
\begin{abstract}
In reliability engineering, data about failure events is often scarce.
To arrive at meaningful estimates for the reliability of a system,
it is therefore often necessary to also include expert information in the analysis,
which is straightforward in the Bayesian approach by using an informative prior distribution.
%
A problem called prior-data conflict then can arise:
observed data seem very surprising from the viewpoint of the prior,
i.e., information from data is in conflict with prior assumptions.
Models based on conjugate priors can be insensitive to prior-data conflict,
in the sense that the spread of the posterior distribution does not increase in case of such a conflict,
thus conveying a false sense of certainty.
%
An approach to mitigate this issue is presented, by considering sets of prior distributions
to model limited knowledge on Weibull distributed component lifetimes,
treating systems with arbitary layout using the survival signature.
This approach can be seen as a robust Bayesian procedure or imprecise probability method
that reflects surprisingly early or late component failures
by wider system reliability bounds.
%We show how surprisingly early or late component failures
%result in wider system reliability bounds.
%
%and study how surprisingly early or late component failures
%affect the prediction of the reliability of a system with arbitrary layout,
%making use of survival signature to characterise the system under study.
%Our approach can be seen as a robust Bayesian procedure or imprecise probability method
%that appropriately reflects surprising data in the posterior system reliability function.
\end{abstract}
% by communicating that we can quantify the reliability of a system quite precisely when in fact we cannot.

@@

\section{Introduction}

In reliability engineering, a central task is to describe the reliability of a complex system.
This is usually done by determining the \emph{reliability function} $R(t)$,
in other contexts also known as the \emph{survival function},
giving the probability that the system has not failed by time $t$:
\begin{align}
\Rsys(t) = P(\Tsys \geq t)\,,
\end{align}
where $\Tsys$ is the random variable giving the failure time of the system. %
%\footnote{}
Based on the distribution of $\Tsys$, which can also be expressed
in terms of the cumulative distribution function $F_\text{sys}(t) = 1 - \Rsys(t)$,
%the density $p_\text{sys}(t)$ or the hazard rate $\lambda_\text{sys}(t)$,
decisions about, e.g., scheduling of maintenance work can be made.

>>>>

\documentclass[Journal,SectionNumbers,InsideFigs]{ascelike}
%\documentclass[Journal,SectionNumbers,SingleSpace,InsideFigs]{ascelike}

@@

%Invited for special issue ``The treatment of uncertainty in risk and reliability modelling and decision making''
%(special issue code SI022A), guest editors Luca Podolfillini, Bruno Sudret, Enrico Zio,
%in ASCE-ASME Journal of Risk and Uncertainty in Engineering Systems: Part A (Civil Engineering)
%
%***``For most ASCE journals, the maximum number of words and word-equivalents is 10,000 for technical papers''
%***Abstract must be 150--175 words long (this has 175), may not contain references or mathematics.
%
\begin{abstract}
In reliability engineering, data about failure events is often scarce.
To arrive at meaningful estimates for the reliability of a system,
it is therefore often necessary to also include expert information in the analysis,
which is straightforward in the Bayesian approach by using an informative prior distribution.
%
A problem called prior-data conflict then can arise:
observed data seem very surprising from the viewpoint of the prior,
i.e., information from data is in conflict with prior assumptions.
Models based on conjugate priors can be insensitive to prior-data conflict,
in the sense that the spread of the posterior distribution does not increase in case of such a conflict,
thus conveying a false sense of certainty.
%
An approach to mitigate this issue is presented, by considering sets of prior distributions
to model limited knowledge on Weibull distributed component lifetimes,
treating systems with arbitrary layout using the survival signature.
This approach can be seen as a robust Bayesian procedure or imprecise probability method
that reflects surprisingly early or late component failures
by wider system reliability bounds.
%We show how surprisingly early or late component failures
%result in wider system reliability bounds.
%
%and study how surprisingly early or late component failures
%affect the prediction of the reliability of a system with arbitrary layout,
%making use of survival signature to characterise the system under study.
%Our approach can be seen as a robust Bayesian procedure or imprecise probability method
%that appropriately reflects surprising data in the posterior system reliability function.
\end{abstract}
% by communicating that we can quantify the reliability of a system quite precisely when in fact we cannot.

@@

\section{Introduction}
\label{sec:intro}
%
In reliability engineering, a central task is to describe the reliability of a complex system.
This is usually done by determining the \emph{reliability function} $R(t)$,
in other contexts also known as the \emph{survival function},
giving the probability that the system has not failed by time $t$:
\begin{linenomath*}
\begin{align}
\Rsys(t) = P(\Tsys \geq t)\,,
\end{align}
\end{linenomath*}
where $\Tsys$ is the random variable giving the failure time of the system. %
%\footnote{}
Based on the distribution of $\Tsys$, which can also be expressed
in terms of the cumulative distribution function $F_\text{sys}(t) = 1 - \Rsys(t)$,
%the density $p_\text{sys}(t)$ or the hazard rate $\lambda_\text{sys}(t)$,
decisions about, e.g., scheduling of maintenance work can be made.
